%\documentclass[twocolumn,amsmath,amssymb]{report}
\documentclass[twocolumn,amsmath,amssymb]{snp}
\pagestyle{empty}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\topmargin 1.5 cm
\textwidth14.5cm
\textheight20cm
\oddsidemargin0.7cm
\columnsep0.2in

\begin{document}

\title{{\Large \LaTeX\ template and guidelines for preparing the manuscript of the invited talks}}% Force line breaks with \\

\author{\large A. Author$^1$}
\email{aauthor@barc.gov.in}
\author{\large B. Author$^2$}
\author{\large C. Author$^3$}
\author{\large D. Author$^4$}%\email{abc@barc.gov.in}
% \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\affiliation{$^1$Nuclear Physics Division, Bhabha Atomic Research Centre, Mumbai - 400085, INDIA}
\affiliation{$^2$Deptartment of Nuclear and Atomic Physics, 
Tata Institute of Fundamental Research, Mumbai - 400005, INDIA}
\affiliation{$^3$Inter University Accelerator Centre, Aruna Asaf Ali Marg, New Delhi - 110067, INDIA}
\affiliation{$^4$Physics Department, XYZ University}




\begin{abstract}
\leftskip1.0cm
\rightskip1.0cm
This is the sample file using \LaTeX\ style for submitting the manuscript of Invited Talks. The sample file for the  
Contribution(s) and Thesis work are available separately. An equivalent MS Word (*.doc file) version of the 
template is also available in  the website for submission of manuscript. The manuscript of the invited 
talk should be of 2 pages of this style. The \LaTeX\ format which has been 
chosen here mostly matches with that of Physical Review C format. The sample file from the aps website has 
been downloaded and modified so as to conform to our Symposium proceeding.
\end{abstract}\maketitle


\section{Introduction}





The size of the figures and tables should not exceed the column width else it can be in two column width. When the figure is too wide for a single column, then use the \texttt{figure*} environment instead. Similarly for wide table one has to use 
\texttt{table*} environment.



\section{Math and Equations}

\section{General Guidelines}



\section*{Acknowledgments}
%\acknowledgments
 We thank you for your co-operation in using this template  for production of camera ready manuscript.
%\end{acknowledgments}

%\ \\
%\noindent
\begin{thebibliography}{50}
\bibitem{poster} Announcement Poster and Website, DAE Symp. {\bf vv}, ppp (yyyy).
\bibitem{dae} DAE Symp. on Nucl. Phys. {\bf vv}, ppp (yyyy).
\end{thebibliography}

\end{document}
%
% ****** End of file snpcontrisamp.tex ******
